Leveraging Diversity to Find Bugs\\ in JavaScript Engines

### 2018-08-25 paper/paper.tex
minor fixes
pass on fixes
final pass

Table~\ref{tab:false-positives} shows the distribution of false
positives per source. The sources of imprecision are as defined in
Section~\ref{sec:transplantation} with the addition of two new
sources, which we did not observe before. These sources are
highlighted with a ``*'' in the table. The source ``Invalid Input''
indicates that the test input violated some part of the
specification. For example, the test indirectly invoked some function
with unexpected arguments; this happens because fuzzing is not
sensitive to function specifications. The source ``Error Message Mismatch''
indicates that 
\Igor{
  o fuzzer realiza mutacoes em assercoes que usam comparacao de string e/ou 
  expressoes regulares.
}

@@

Table~\ref{tab:bugs} shows the list of bugs we reported. The table
shows the date the bug was reported (``Date''), the fuzzing tool used
(``Fuzz''), the \js\ engine affected (``Engine''), the status of the
bug report as of Aug. 24, 2018 (``Status''), the Url of the bug report
(``Url''), the severity of the bug report (``Severity''), the priority
that we assigned to the warning that revealed the bug (``Priority''),
and the test suite from the original test input (``Suite''). So far,
\noDiffConfirmed{} of the bugs we reported were confirmed, \noDiffFixed{} of which
were fixed. Note that one bug report that we submitted was rejected on
the basis that the offending JS file manifested an incompatibility
across engine implementations that was considered to be acceptable. As
of now, we did not find any new bugs on \smonkey{}; the bugs we found
were duplicates and were not reported. In \veight{}, we reported two
bugs, both of which were confirmed, with one fixed.

@@

%%  LocalWords:  bytecodes JScript Ecma ome IoT Kangax DT JS fuzzer
%%  LocalWords:  jsfunfuzz jit funfuzz \smonkey{} toPrecision JSVU
%%  LocalWords:  GoogleChromeLab's cccr js runtime Fuzzers Radamsa de
%%  LocalWords:  QuickFuzz fuzzers Grammarinator LangFuzz Megadeth
%%  LocalWords:  AFL libFuzzer toolchain sanitizers arrowed eshost
%%  LocalWords:  cli pre EcmaScript dataset piecharts piechart \chakra{}
%%  LocalWords:  JavascriptCore Url radamsa TinyJS \jerry{} JSC crr
%%  LocalWords:  quickfuzz \jsc{} \chakra{}'s valueOf NUL ascii crrrr
%%  LocalWords:  unary ToNumber NaN testcase WebKit typeof foofoofoo
%%  LocalWords:  SSL TLS ICSE ReferenceError TypeError lineNumber
%%  LocalWords:  drainMicrotasks subtrees ArrayBuffer RangeError eval
%%  LocalWords:  ToIndex Clusterization DataView setInt getInt boxpos
%%  LocalWords:  JavaScriptCore SpiderMonkey byteOffset anonymized
%%  LocalWords:  xleftmargin framexleftmargin basicstyle numberstyle
%%  LocalWords:  escapeinside morekeywords

>>>>

Table~\ref{tab:false-positives} shows the distribution of false
positives per source. The sources of imprecision are as defined in
Section~\ref{sec:transplantation} with the addition of two new
sources, which we did not observe before. These sources are
highlighted with a ``*'' in the table. The source ``Invalid Input''
indicates that the test input violated some part of the
specification. For example, the test indirectly invoked some function
with unexpected arguments; this happens because fuzzing is not
sensitive to function specifications. Consequently, it can replace
valid with invalid inputs. The source ``Error Message Mismatch''
corresponds to the cases where the fuzzer modifies the assertion
expression (\eg{}, some string expression or regular expression).

@@

Table~\ref{tab:bugs} shows the list of bugs we reported. The table
shows the date the bug was reported (``Date''), the fuzzing tool used
(``Fuzz''), the \js\ engine affected (``Engine''), the status of the
bug report as of Aug. 24, 2018 (``Status''), the Url of the bug report
(``Url''), the severity of the bug report (``Severity''), the priority
that we assigned to the warning that revealed the bug (``Priority''),
and the test suite from the original test input (``Suite''). So far,
\noDiffConfirmed{} of the bugs we reported were confirmed, \noDiffFixed{} of which
were fixed. Note that one bug report that we submitted was rejected on
the basis that the offending JS file manifested an incompatibility
across engine implementations that was considered to be acceptable. As
of now, we did not find any new bugs on \smonkey{}; the bugs we found
were duplicates and were not reported. Considering \veight{}, we reported two
bugs, both of which were confirmed, with one fixed.

@@

%%  LocalWords:  bytecodes JScript Ecma ome IoT Kangax DT JS fuzzer
%%  LocalWords:  jsfunfuzz jit funfuzz \smonkey{} toPrecision JSVU os
%%  LocalWords:  GoogleChromeLab's cccr js runtime Fuzzers Radamsa de
%%  LocalWords:  QuickFuzz fuzzers Grammarinator LangFuzz Megadeth
%%  LocalWords:  AFL libFuzzer toolchain sanitizers arrowed eshost
%%  LocalWords:  cli pre EcmaScript dataset piecharts piechart \chakra{}
%%  LocalWords:  JavascriptCore Url radamsa TinyJS \jerry{} JSC crr
%%  LocalWords:  quickfuzz \jsc{} \chakra{}'s valueOf NUL ascii crrrr
%%  LocalWords:  unary ToNumber NaN testcase WebKit typeof foofoofoo
%%  LocalWords:  SSL TLS ICSE ReferenceError TypeError lineNumber sep
%%  LocalWords:  drainMicrotasks subtrees ArrayBuffer RangeError eval
%%  LocalWords:  ToIndex Clusterization DataView setInt getInt boxpos
%%  LocalWords:  JavaScriptCore SpiderMonkey byteOffset anonymized
%%  LocalWords:  xleftmargin framexleftmargin basicstyle numberstyle
%%  LocalWords:  escapeinside morekeywords cccrr ccrrrr Duktape JSI
%%  LocalWords:  Lembrar que
